---
title: "DV_RProject 3"
output: html_document
---

Our data set is based off of a culmination of data compiled from employees who have worked for the railroad. 

**members:** Andrea Curo, Dora Cheng, Sonam Shah

#Head subset of data
```{r fig.width=10, fig.height=10}
source("../01 Data/data.R", echo= TRUE)
```

#Data wrangling sets and Coordinating Visualizations
###Different Alertness Levels Compared to Average Caffeine LEvel
```{r fig.width=10, fig.height=10}
#source("../02 Data Wrangling/df_alertness_caffeine.R", echo= TRUE)
```

###Different Alertness Levels Compared to Schedule Type
```{r fig.width=10, fig.height=10}
source("../02 Data Wrangling/df_alertness_schedtype.R", echo= TRUE)
```

###Sleep Quality Compared to Activity Type
```{r fig.width=10, fig.height=10}
#source("../02 Data Wrangling/df_sleep_activity.R", echo= TRUE)
```

###Sleep Quality and Length Compared to Job Length
```{r fig.width=10, fig.height=10}
source("../02 Data Wrangling/df_sleep_joblength.R", echo= TRUE)
```